---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# slackposts

<!-- badges: start -->
[![Covrpage Summary](https://img.shields.io/badge/covrpage-Last_Build_2020_08_13-brightgreen.svg)](http://tinyurl.com/qq3vz59)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-win build status](https://github.com/yonicd/slackposts/workflows/R-win/badge.svg)](https://github.com/yonicd/slackposts)
[![R-mac build status](https://github.com/yonicd/slackposts/workflows/R-mac/badge.svg)](https://github.com/yonicd/slackposts)
[![R-linux build status](https://github.com/yonicd/slackposts/workflows/R-linux/badge.svg)](https://github.com/yonicd/slackposts)
[![Codecov test coverage](https://codecov.io/gh/yonicd/slackposts/branch/master/graph/badge.svg)](https://codecov.io/gh/yonicd/slackposts?branch=master)
<!-- badges: end -->

`slackposts` is a part of `slackverse`

```{r,echo = FALSE, eval = TRUE}
pkgs <- sprintf('slack%s',c('calls','teams','posts','blocks','threads','reprex'))

badges <- sprintf('%s<br>[![](https://github.com/yonicd/%s/workflows/R-mac/badge.svg)](https://github.com/yonicd/%s)',pkgs,pkgs,pkgs)

names(badges) <- pkgs

```

||||
|:-:|:-:|:-:|
||`r badges[pkgs[1]]`<br>`r emo::ji('down_left_arrow')``r emo::ji('down_arrow')``r emo::ji('down_right_arrow')`||
|`r badges[pkgs[5]]`|`r badges[pkgs[2]]`<br>`r emo::ji('left_arrow')``r emo::ji('down_right_arrow')`|`r badges[pkgs[3]]`<br>`r emo::ji('down_arrow')`|
|||`r badges[pkgs[4]]`<br>`r emo::ji('down_arrow')`|
|||`r badges[pkgs[6]]`|

`slackposts` is an `R` package that allows the user to manage multiple Slack teams during a session. 

## Installation

``` r
remotes::install_github("yonicd/slackposts")
```
